Holomorphic field theories and higher algebra

### 2022-07-15 draft.tex
revisions of seiberg section

\section{Holomorphic $\sigma$-models, higher algebras of differential operators, and free field realization}

@@

The field content of 4d $\cN=1$ supersymmetric Yang--Mills theory is:
\begin{itemize}
\item a `vector multiplet' which consists of a gauge field $A$ together with some fermions $\lambda$ all taking values in a Lie algebra $\fg$;
\item a `matter multiplet' (usually called the chiral multiplet) which consists of a scalar $\phi$ together with some fermions $\psi$ all transforming in some representation $V$ of $\fg$. 
Additionally, there is a `superpotential' $W$ which is a $\fg$-invariant polynomial on~$V$. 
\end{itemize}

From hereon we fix a nonzero, square zero supercharge of the 4d $\cN=1$ supersymmetry algebra for which we wish to twist by. 
The twist of 4d $\cN=1$ supersymmetric Yang--Mills theory has been characterized in \cite{CosYangian, ESW, SWchar}. 
It is a holomorphic field theory on $\CC^2$ consisting of a `vector' part and a 'matter' part.
As a moduli space, it can be described in the following way (we will give a description in terms of fields and action functionals afterwards).

@@

Our long term goal is to show that two special cases of holomorphic QCD are {\em dual}.
We focus on the gauge group $G = \SU(N)$, and consider a class of holomorphic QCD theories associated to particular choices of representations and superpotential. 
Following physics terminology, will refer to the defining $N$-dimensional representation $\CC^N$ of $\SU(N)$ as the {\em fundamental} representation. 
Also, suppose $N_c, N_f$ are integers with $N_f \geq N_c \geq 2$.
%Also, let $N_{\rm mes} \geq 0$ be some integer.  
%{\em Type A} holomorphic QCD is 
%\[
%\cT_{A} (N_c, N_f, N_{\rm mes},W) = \cT\left(G = \SU(N_c) \, , \, V = (\CC^{N_c})^{\oplus N_f} \, , \, Z = \CC^{\oplus N_{\rm mes}} \, , \, W\right) .
%\]

@@

\begin{thm}
Both $\cT_{\sfE}(N_c, N_f)$ and $\cT_{\sfM}(N_c, N_f)$ exist at the quantum level. 
That is, the anomaly to a perturbative BV quantization vanishes.
In fact, the quantization is one-loop exact. 
\end{thm}

@@

The statement should be interpreted as an equivalence of factorization algebras valued in $\ZZ/2$-graded cochain complexes since the field theories are only $\ZZ/2$ graded.
We fix some notation for the fields of the electric and magnetic theories. 
The `flavor' index will be denoted by letters $i,j=1,\ldots, N_f$.

@@

We start off with the (complexified) 4d $\cN=1$ superconformal algebra $\sl(4|1)$.
This super Lie algebra is the defining symmetry of a 4d $\cN=1$ superconformal field theory. 
The Poincar\'{e} algebra is a subalgebra of $\sl(4|1)$. %which in particular consists of supercharges $\cQ_{\alpha}, \cQ_{\dot{\alpha}}$ where $\alpha = 1,2$ is an $\SU(2)$ index.
Inside of this algebra is the Cartan generator $\Delta$ of scaling transformations in $\RR^4$.

@@

>>>>

\section{Holomorphic $\sigma$-models, higher algebras of differential operators, and higher free field realization}

\owen{We should also discuss how these can reduce to LG B-models, as precursor to the Hori-Tong dualities.}

@@

A major endeavor in theoretical physics is to develop a deep and effective understanding of theories like quantum chromodynamics (QCD), which governs the behavior of quarks and gluons.
One natural approach is to study theories that are close cousins but that are easier to analyze,
and a notable way is to look for theories with the same ingredients but with larger groups of symmetries.
Supersymmetric Yang--Mills theories are quite appealing in this regard,
and there have been remarkable successes in this direction.
A well-known high point is the work of Seiberg and Witten on 4-dimensional $\cN =2$ supersymmetric Yang--Mills theory,
where they explained how confinement could be realized by a version of the Mandelstam-'t Hooft mechanism (i.e., a kind of electromagnetic duality identifies confinement with a Meissner-type effect).
Their work offered powerful new tools that opened up much subsequent progress,
and even impacted mathematics through the Seiberg-Witten equations (which is related to the topologically twisted versions of $\cN=2$ theory).

The class of supersymmetric theories closest to the Standard Model, however, has only $\cN=1$ supersymmetry.
There too Seiberg offered inspiring and powerful insights typically referred to as {\em Seiberg duality}.
These ideas have had a large impact in theoretical physics \owen{give the citation number on that paper},
but the impact in mathematics is much more muted,
possibly due to the lack of a topological twist of $\cN=1$ theories.
Such theories do admit {\em holomorphic} twists, however, 
and so we explore here what holomorphic Seiberg duality might mean and what its consequences could be in mathematics.
In our opinion this direction could be quite fruitful and we welcome others to join us in exploring it.

We begin this section by describing the holomorphic twist of $\cN=1$ supersymmetric Yang--Mills theory,
and then we offer a holomorphic version of Seiberg duality, 
initially conjectured by Richard Eager.
We explain our first efforts in this direction and how it offers evidence for the conjecture;
we then refine Eager's version.
We also explain how this duality, when compactified along Riemann surfaces,
should produce equivalences between different kinds of 2-dimensional B-model theories;
these reductions are related to work of Hori and Hori--Tong \owen{citations} and its mathematical development by Ed Segal, \owen{list others}.

\subsection{Holomorphic QCD}

The field content of 4-dimensional $\cN=1$ supersymmetric Yang--Mills theory is:
\begin{itemize}
\item a `vector multiplet' which consists of a gauge field $A$ together with some fermions $\lambda$ all taking values in a Lie algebra $\fg$;
\item a `matter multiplet' (usually called the chiral multiplet) which consists of a scalar $\phi$ together with some fermions $\psi$ all transforming in some representation $V$ of $\fg$. 
Additionally, there is a `superpotential' $W$ which is a $\fg$-invariant polynomial on~$V$. 
\end{itemize}

From hereon we fix a nonzero, square zero supercharge of the 4-dimensional $\cN=1$ supersymmetry algebra for which we wish to twist by. 
The twist of 4-dimensional $\cN=1$ supersymmetric Yang--Mills theory has been characterized in \cite{CosYangian, ESW, SWchar}. 
It is a holomorphic field theory on $\CC^2$ consisting of a `vector' part and a 'matter' part.
As a moduli space, it can be described in the following way (we will give a description in terms of fields and action functionals afterwards).

@@

\subsection{A first pass at Seiberg duality}

Our long-term goal is to show that two special cases of holomorphic QCD are {\em dual}.
The notion of duality can refer to several kinds of relationships,
but loosely speaking it means that some aspects of the two theories are equivalent under some dictionary or correspondence.
We will postpone saying something precise till we have some terminology in place.

We focus on the gauge group $G = \SU(N)$, and consider a class of holomorphic QCD theories associated to particular choices of representations and superpotential. 
Following physics terminology, we will refer to the defining $N$-dimensional representation $\CC^N$ of $\SU(N)$ as the {\em fundamental} representation. 
Also, let $N_c, N_f$ denote integers where $N_f \geq N_c \geq 2$.
%Also, let $N_{\rm mes} \geq 0$ be some integer.  
%{\em Type A} holomorphic QCD is 
%\[
%\cT_{A} (N_c, N_f, N_{\rm mes},W) = \cT\left(G = \SU(N_c) \, , \, V = (\CC^{N_c})^{\oplus N_f} \, , \, Z = \CC^{\oplus N_{\rm mes}} \, , \, W\right) .
%\]

@@

The usual Seiberg duality states how certain ``electric'' and ``magnetic'' versions of SQCD ($\cN=1$ supersymmetric QCD) should be equivalent.
Our electric and magnetic holomorphic QCDs are precisely the holomorphic twists of those that appear in Seiberg duality.
In \cite{Eager} Richard Eager suggested that Seiberg duality should survive after taking the holomorphic twist.

@@

The statement should be interpreted as an equivalence of factorization algebras valued in $\ZZ/2$-graded cochain complexes since the field theories are only $\ZZ/2$-graded.

One appealing aspect of Eager's conjecture is that it is mathematically precise:
duality would mean giving an equivalence of factorization algebras.
It is analogous to claiming that two vertex algebras are equivalent,
such as in the well-known boson-fermion correspondence.
In this sense it is a target at which a mathematician can aim,
rather than the more amorphous statements of duality that one often finds in the physics literature.
In that literature, however, there is guidance on what map of factorization algebras provides the equivalence,
which we describe in the next section.

In general, Eager's suggestion opens up a fascinating vein of inquiry:
\begin{quote}
how do physical results about supersymmetric gauge theories behave under twisting?
\end{quote}
We have found, so far, that they often admit clean mathematical formulations and that the holomorphic (or topological) twists involve constructions of natural interest in geometry and representation theory.
In \cite{EGW} we and Chris Elliott explored twists of $\cN=4$ supersymmetric Yang--Mills theory,
provided their quantizations, and began analyzing their factorization algebras.
Following Eager, we can ask about the twisted versions of S-duality and how to provide those conjectured equivalences.

\subsection{Evidence for holomorphic Seiberg duality}

We now turn to examining evidence for the conjecture, which will, in turn, allow us to refine it.
The first piece of evidence involves the classical field theories:
\begin{quote}
$\bullet$ Each theory has a moduli stack of vacua, and there is a natural isomorphism between \owen{the affinizations?} the spaces for theories dual according to the conjecture.
\end{quote}
This map of stacks determines a map of factorization algebras of classical observables,
and it should deform to the map between the factorization algebras for the quantum theories.
As we discuss in a moment, holomorphic QCD can be quantized using the techniques of \cite{BW work}.
There are then two further pieces of evidence when these quantum theories are examined:
\begin{enumerate}
\item There are {\em flavor} symmetries that act on each theory, and these can be matched under the duality. Under quantization, these have isomorphic anomalies.
\item There are {\em spacetime} symmetries that act on each theory, notably isometries, and on the classical holomorphic theories, these enhance to an action of holomorphic vector fields. Under quantization, these have isomorphic anomalies.
\end{enumerate}
This triple of evidence is analogous (and sometimes stronger) than results for Seiberg duality for SQCD. 
We now turn to fleshing out the assertions above.

\subsubsection{Moduli of vacua and quantization}

It is fruitful, and standard in physics, to identify the simplest solutions to the equations of motion for a theory.
Here that means a solution that is translation-invariant on $\CC^2$ (i.e., a constant solution),
and we call such a solution a {\em classical vacuum}.
Thus each theory has an associated {\em moduli space of classical vacua},
which we describe in the next subsection.
Each vacuum determines a perturbative field theory that one could try to quantize,
and we have shown the following.
(Many arguments are close cousins of~\cite{EGW}, where we quantize every twist over a moduli of vacua of the $\cN=4$ supersymmetric Yang--Mills theory.)

\begin{thm}
Both $\cT_{\sfE}(N_c, N_f)$ and $\cT_{\sfM}(N_c, N_f)$ exist at the quantum level for any choice of classical vacuum. 
That is, the anomaly to a perturbative BV quantization vanishes.
In fact, the quantization is one-loop exact. 
\end{thm}

We fix some notation for the fields of the electric and magnetic theories. 
The `flavor' index will be denoted by letters $i,j=1,\ldots, N_f$.

@@

We start off with the (complexified) 4-dimensional $\cN=1$ superconformal algebra $\sl(4|1)$.
This super Lie algebra is the defining symmetry of a 4-dimensional $\cN=1$ superconformal field theory. 
The Poincar\'{e} algebra is a subalgebra of $\sl(4|1)$. %which in particular consists of supercharges $\cQ_{\alpha}, \cQ_{\dot{\alpha}}$ where $\alpha = 1,2$ is an $\SU(2)$ index.
Inside of this algebra is the Cartan generator $\Delta$ of scaling transformations in $\RR^4$.

@@

\subsection{A second pass at holomorphic Seiberg duality, and its relations to Hori-Tong duality}
